---
title: "eds-212-day-Tasks"
---

```{r}
library(tidyverse)
library(palmerpenguins)
```

-   In your Quarto document, find the derivative expression and slope at the indicated value for each the following functions in R (each in a separate code chunk).

    1.  Find the slope of f(x)=x2 at x=3

    2.  Find the slope of P(a)=2(3a+2)4−5 at a=1.2

```{r}
fx = D(expression(x ^ 2), "x")
x <- 3

eval(fx)
```

```{r}
# P(a)=2(3a+2)^4 -5 at a = 1.2

fx = D(expression(2 * (3 * a + 2)^4 - 5), "a")
a <- 1.2

eval(fx)
```

## ggplot

-   In a new code chunk, create a `ggplot` graph of penguin bill length versus bill depth (using the `penguins` dataset in the `palmerpenguins` package), with point color dependent on species. You should attach the `tidyverse` and`palmerpenguins` package in your .qmd setup chunk if you haven\'t already. Update labels and add a title.

-   In a new code chunk, make a jitter plot of flipper length by species (species on the x-axis, flipper length on the y-axis). Update axis labels and add a title. See ?geom_jitter

-   Render your .qmd to check for reproducibility

-   Stage, commit, and push changes to the remote repo. Once you do, go to GitHub and check to see the changes are safely stored & tracked.

-   Go back to your Quarto document in RStudio. Pull to make sure you have the same versions as in the remote repo. Make a change (anything you want - maybe change your graph colors, sizes, etc.), then stage, commit, & push changes to the remote repo to reinforce the steps. Check that changes are stored on GitHub.

-   Repeat two more times - make changes to your plot, knit, stage, commit & push. Check that your changes appear on GitHub.

```{r}
library(tidyverse)
library(palmerpenguins)
```

```{r}

ggplot(data.frame(penguins), aes(x = bill_length_mm, 
                                 y = bill_depth_mm, 
                                 color = species)) +
  geom_point() + labs(title = "Penguins bill length versus bill depth", 
                      x = "Bill length, mm", 
                      y = "Bill depth, mm")
  
```

-   In a new code chunk, make a jitter plot of flipper length by species (species on the x-axis, flipper length on the y-axis). Update axis labels and add a title. See ?geom_jitter

```{r}

ggplot(data.frame(penguins), aes(x = species, 
                                 y = flipper_length_mm, 
                                 color = species)) +
  geom_jitter() + labs(title = "Penguins flipper length by species", 
                      x = "Penguine species", 
                      y = "Flipper Length, mm")
```
